Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-09-29 analysis/paper/Rmd/hotspots-paper.Rmd
fixed url for attie data

```{r saveRDS}
if (!file.exists(here::here("analysis", "data", "derived_data", "genoprobs.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here::here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here::here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here::here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here::here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here::here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here::here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here::here("analysis", "data", "derived_data", "covar.rds"))
}
```

>>>>

```{r saveRDS}
if (!file.exists(here::here("analysis", "data", "derived_data", "genoprobs.rds"))){
  download.file("https://datadryad.org/stash/downloads/file_stream/63306",
              destfile = here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here::here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here::here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here::here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here::here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here::here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here::here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here::here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here::here("analysis", "data", "derived_data", "covar.rds"))
}
```
